---
output: github_document
format: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Awesome R-Ladies' Content and Packages

[![Awesome](https://awesome.re/badge.svg)](https://awesome.re)

Curated lists of R-Ladies community resources (blogs, YouTube channels, and R packages currently). 
Each entry is stored as a JSON metadata file in this repository; the site-friendly aggregated JSON files are generated into the `website/` directory by the script `scripts/generate_website_jsons.R`.

To contribute: add a JSON file describing the blog (to `content/`) or the package (to `packages/`) following the examples in the repository and the JSON schema at `scripts/json_schema/`.

See `CONTRIBUTING.md` for style and metadata conventions.

## List of blogs

Created from the JSON files in `data/content/` (one JSON per blog). The aggregated file is written to `data/website/awesome_content.json`.
```{r, echo = FALSE, results='asis'}
json_list <- list.files(here::here("data/content"), "json$", full.names = TRUE)
dt <- lapply(json_list, jsonlite::read_json)

invisible(
  lapply(dt, function(x) {
    cat(
      sprintf(
        " - [%s](%s) by %s",
        x$title,
        x$url,
        paste(sapply(x$authors, function(x) x$name), collapse = ", ")
      ),
      sep = "\n"
    )
  })
)
```

## List of packages

Created from the JSON files in `data/packages/` (one JSON per package). The aggregated file is written to `data/website/awesome_packages.json`.
```{r, echo = FALSE, results='asis'}
json_list <- list.files(here::here("data/packages"), "json$", full.names = TRUE)
dt <- lapply(json_list, jsonlite::read_json)

invisible(
  lapply(dt, function(x) {
    cat(
      sprintf(
        " - [%s](%s) by %s",
        x$name,
        x$repo_url,
        paste(sapply(x$maintainers, function(x) x$name), collapse = ", ")
      ),
      sep = "\n"
    )
  })
)
```


## License

[![CC0](https://upload.wikimedia.org/wikipedia/commons/6/69/CC0_button.svg)](https://creativecommons.org/publicdomain/zero/1.0/)

